Measuring Subgroup Preferences in Conjoint Experiments

### 2019-05-06 manuscript.Rnw
update README

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}

>>>>

\title{Measuring Subgroup Preferences in Conjoint Experiments%\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}
}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}

### 2019-05-06 manuscript.tex
update README

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

>>>>

\title{Measuring Subgroup Preferences in Conjoint Experiments%\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}
}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
